\documentclass[12pt,english]{article}

\usepackage{natbib}

\usepackage{graphics,graphicx,dcolumn,bm,fleqn,epic,eepic,float}
\usepackage{amssymb,amsmath,multirow,rotate,rotating,color}
\usepackage[utf8]{inputenc}

\usepackage[english]{babel}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
%\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\tikzset{fontscale/.style = {font=\relsize{#1}}}
\usetikzlibrary{calc}
\makeatother

\newcommand{\figref}[1]{Fig.~\ref{fig:#1}}
\newcommand{\eqnref}[1]{Eq.~(\ref{eq:#1})}
\newcommand{\ts}{\textsuperscript}

\definecolor{tuered}{RGB}{214,0,74}

\newcommand{\todo}[1]{\textbf{\textcolor{tuered}{ TODO: #1}}}

\newcommand{\vectornorm}[1]{\left|\left|#1\right|\right|}

\renewcommand{\vec}[1]{\mathbf{#1}}
\newcommand{\uvec}[1]{\hat{\vec{#1}}}
\newcommand{\tensor}[1]{\mathbf{#1}}

\definecolor{pyblue}{HTML}{1F77B4}
\definecolor{pyorange}{HTML}{FF7F0C}
\definecolor{pygreen}{HTML}{2CA02C}
\definecolor{pyred}{HTML}{D62728}

\newcommand{\JH}[1]{\textcolor{blue}{JH: #1}}
\begin{document}

\noindent Dear Editor,\\
\\
\noindent We gratefully thank you for sending us the reports on our manuscript. We are glad to see 
that the Referees agree that the work is interesting and scientifically relevant, with one of them 
(Referee B) inclined to accept it. 
We have made a major revision taking into account all Referees' reasonable remarks, including novel 
results from new simulations and theoretical derivations (see the new Supplementary Material).
Let us, please, stress further how and why we deem that the present paper meets the Physical
Review Letters criteria of impact and innovation (interest, as we already noted, was acknowledged by the Referees).
We have found a novel effect in the dewetting on substrates with properly tailored time dependent properties, and 
suggested how to exploit it to control the dewetting morphologies. 
We think that the impact of this discovery is out of question, as witnessed by the various publications, also on in PRL on dewetting and closely related problems
(just to cite but a few recent ones: J.C. Fern\'andez-Toledano et al, ``How wettability controls nanoprinting'',
{\it Phys. Rev. Lett.} {\bf 124} 224503 (2020); A.A. Pahlavan et al,
``Evaporation of binary-mixture liquid droplets: the formation of picoliter pancakelike shapes'', {\it Phys. Rev. Lett.} {\bf 127}, 024501 (2021); 
C. Clavaud et al, ``Modification of the fluctuation dynamics of ultrathin wetting films'', {\it Phys. Rev. Lett.} {\bf 126}, 228004 (2021)).
What it is questionable here, instead, is the reliability of some of the Referees in judging a paper on microscale multiphase fluid dynamics: one of 
them (Referee A) ignores the concept of disjoining pressure, confuses dewetting with prewetting and concepts from the physics of free surface flows to wetting.
The main ``argument'' of Referee C against publication is that he/she does not see ``how would the transport of a fluid by rivulets 
surpass the transport by droplets''; but the paper is about controlling morphologies, not about transport.
On the other hand, we acknowledge that certain points were not explained and/or discussed adequately, so we have put a lot of effort in clarifying all
doubts and concerns. 
Therefore, we would like to bring to your attention again our manuscript in its new form, confident that it might now be suitable to appear in Physical Review Letters.\\
\\
With our best regards,\\
the Authors.

\end{document}
