\documentclass[12pt,english]{article}

\usepackage{natbib}

\usepackage{graphics,graphicx,dcolumn,bm,fleqn,epic,eepic,float}
\usepackage{amssymb,amsmath,multirow,rotate,rotating,color}
\usepackage[utf8]{inputenc}

\usepackage[english]{babel}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
%\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\tikzset{fontscale/.style = {font=\relsize{#1}}}
\usetikzlibrary{calc}
\makeatother

\newcommand{\figref}[1]{Fig.~\ref{fig:#1}}
\newcommand{\eqnref}[1]{Eq.~(\ref{eq:#1})}
\newcommand{\ts}{\textsuperscript}

\definecolor{tuered}{RGB}{214,0,74}

\newcommand{\todo}[1]{\textbf{\textcolor{tuered}{ TODO: #1}}}

\newcommand{\vectornorm}[1]{\left|\left|#1\right|\right|}

\renewcommand{\vec}[1]{\mathbf{#1}}
\newcommand{\uvec}[1]{\hat{\vec{#1}}}
\newcommand{\tensor}[1]{\mathbf{#1}}

\definecolor{pyblue}{HTML}{1F77B4}
\definecolor{pyorange}{HTML}{FF7F0C}
\definecolor{pygreen}{HTML}{2CA02C}
\definecolor{pyred}{HTML}{D62728}

\newcommand{\JH}[1]{\textcolor{blue}{JH: #1}}
\begin{document}

% The referee PDF has been generated from r239 -- 'make referee' command.

\section*{Reply to Referee D}
We thank the new Referee for his/her report on our manuscript. 
We are glad to read that he/she acknowledges the systematic approach we have taken and are happy to see that he/she finds our results interesting. 
We understand the concerns raised by the referee and wonder why the recommendation is negative.
Hereafter, we provide answers to the various questions/comments raised. 
All changes in the revised version are reported in red color.

\begin{itemize}

\item[ \textbf{\underline{Comment 1.}}]
{ 
It seems impossible to construct the patterns described by Equation (3) in a real experiment, making the current research less attractive.
}

\item[ \textbf{{Answer}}]
{
We are very surprised by this comment and do not agree with the assessment of the referee. 
% For static patterns it is well known how to pattern substrates in a precise and controlled way using, e.g. lithography. 
It is true that the novelty of the here presented work is strongly coupled to both the temporal and spatial component of the wettability and as such to equation (3).
We are certain that switchable substrates offer this kind of control, and for photoswitchable materials spiropyran should be a perfect candidate~\cite{keyvanradSpiropyranbasedAdvancedPhotoswitchable2022}. 

Not only do we present our numerical and analytical results in this letter, but we also supply a potential realization for a lab experiment. 
We provide a schematic setup using a photoswitchable substrate and a digital multimirror device. 
As we are well aware that this is not sufficient for an experiment we further identify the relevant length and time scales for both the film and the apparatus.
% Hoping that experimentalist confirm transition we supply a way to construct pattern Eq. (3).
%We therefore have a hard time understanding why it seems impossible to the referee to construct the pattern equation %(3), as he/she does not give us a single increment of information in his/her comment.
}

\item[ \textbf{\underline{Comment 2.}}] 
{
This work is completed based on the lubrication equation for the thin film flows.
From theoretical/mathematical aspects, the novelty of this work, in my opinion, is not strong enough. 
This lubrication model employed here was proposed about 40 years ago and has been thoroughly investigated~\cite{RevModPhys.69.931, RevModPhys.81.1131}. 
There are no improvements or modifications to the model in this work. 
Additionally, the model for the rupture time comes from a simple scaling analysis, which is not very convincing when considering other classical mathematical approaches, such as linear instability analysis, similarity transformation, etc.
}

\item[ \textbf{{Answer}}]
{
We find it puzzling that the referee arrives at the conclusion that working on a theory which is 40 years old does not allow for the novelty attributed to PRL.
A good counter example is: M. Wilczek et al,
"Sliding drops – ensemble statistics from single drop bifurcations", {\it Phys. Rev. Lett.} {\bf 119}, 204501 (2017), in which Wilczek et al. use the thin film equation on an inclined plane.
Similar arguments can be constructed about the Navier-Stokes equation which is 180 years old, still there is a lot of research dedicated towards, e.g., turbulence.

We agree with the referee that from a purely mathematical point of view lubrication theory is untouched.
There is no reason or advantage to add artificial complexity to a well working theory which has been developed for this singular purpose.
However, when it comes to dynamical effects and non-linear behaviour of thin films, the topic this letter revolves around, mathematics falls short and only numerical simulation or experiments offer deeper insights.
To this end we use a novel lattice Boltzmann method to solve the thin film equation at time scales where initial small perturbations have grown to similar sizes as $h_0$.
It is well known that the rupture time marks the end of the linear regime and linear instability theory as suggested by the referee, which has been used in our previous work~\cite{PhysRevE.104.034801}. 
However, it is simply not able to explain our observations, as $\tau_r$ is dependent on $\Gamma$. 
Observing the morphological transition during dewetting from a droplet to a rivulet state is by no means covered by linear analysis. 
It is a dynamic competition of relevant velocities which to the best knowledge of the authors has not been discussed or shown before.
}

\item[ \textbf{\underline{Comment 3.}}]
{
The mobility function in Equation (1) contains the slip length $\delta$. 
But there is no further information in this work. 
Is the slip length of a patterned substrate constant? 
If so, it is quite unreasonable because a hydrophobic substrate is usually more slippery than a hydrophilic one. 
Moreover, previous works had showed that the slip is crucial to the interface dynamics~\cite{zhang_sprittles_lockerby_2021, zhao_zhang_si_2023}, which should be taken into account.
}

\item[ \textbf{{Answer}}]
{
We thank the Referee for this remark. It is of course true that the slip length 
should grow with the contact angle, on the other hand it is also well known that for low contact angle (actually up to $\sim 100^{\circ}$) such dependence is relatively weak, 
as it is expected to follow the relation $\lambda \propto (1+\cos \theta)^{-2}$
(see Huang et al, {\it Phys. Rev. Lett.} {\bf 101}, 226101 (2008)). The ratio 
of the slip lengths on patches of contanct angles $10^{\circ}$ and $30^{\circ}$
(which is the case of our simulations), for instance, would then be $\approx 0.9$,
such that the slip length should have been varied between $0.95$ and $1.05$ lbu. We deemed, then, reasonable to consider it approximately constant. 
To provide an idea, in reference~\cite{zhang_sprittles_lockerby_2021}, for instance, effects were appreciated 
when slip lengths were two to five times larger than each other. 
}

\item[ \textbf{\underline{Comment 4.}}]
{ 
According to the fluid parameters displayed in the supplemental material, the initial thickness of the film is about 4 nm. 
Thermal fluctuations had been shown to play a key role at this scale~\cite{PhysRevLett.99.114503, PhysRevLett.126.228004}, which might affect the dynamics seriously.
}

\item[ \textbf{{Answer}}]
{
We do not say that the initial film thickness is $4 \, \text{nm}$, we just considered the experiments of Becker et al (where the initial film thickness is $\sim 4 \, \text{nm}$) as a reference, since they provide experimental values of quantities (such as the Hamaker constant) that enable the comparison 
with the numerics. The effect of thermal fluctuations, though, is known to essentially show up as 
a speed up of the growth of the instability, but it does not affect particularly the dewetting morphology (as shown in Becker et al, {\it Nat. Mater.} {\bf 2}, 59--63, who made direct comparison 
of the numerical simulation of a lubrication model with experiments).
}


\end{itemize}


\bibliographystyle{abbrv}
\bibliography{Ref}

\end{document}
